### 2021-03-22 Chapter-1/Chapter-1.tex
Updates from Overleaf

Among them, address-based side channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially common and have been studied for years~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}. These
attacks result from vulnerable software and shared hardware components.
By observing program outputs or hardware behaviors, attackers can infer program
execution flows that manipulate secrets and guess secrets such as encryption
keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.

>>>>

Among them, address-based side-channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially common and have been studied for years~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}. These attacks result from vulnerable software and shared hardware components between the attacker and the victim.
By observing program outputs or hardware behaviors, attackers can infer program execution flows that manipulate secrets and guess secrets such as encryption keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.
